%% CV - Wuzzuf_technical_lead_full_stack_developer, Technical Lead – Full Stack Developer
%% Tailored by tailor.py from data/jobs.json

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Mohamed Zahran - CV - Wuzzuf_technical_lead_full_stack_developer},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.77]{geometry}
\usepackage{import}
\usepackage{needspace}

\name{Mohamed Osama}{Zahran}
\address{Cairo, Egypt}{}{}
\phone[mobile]{+20 109 208 8922}
\email{mohamedzahrann0@gmail.com}
\extrainfo{\href{https://linkedin.com/in/mohamed-zahrann}{LinkedIn}, \href{https://mohamedzahran.vercel.app}{Portfolio}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Software Engineer with production experience building AI-integrated full-stack web applications with React, Next.js at the senior / lead level. Specialises in component-driven, accessible interfaces forremote-first SaaS environments, with hands-on experience integrating large language models, voice AI, and NLP pipelines (HuggingFace, Gemini, VAPI) into customer-facing products. Maintainer of Turjuman, an open-source Arabic AI document-translation platform. Comfortable moving between frontend (React, Next.js, TypeScript) and backend-adjacent work (Python, FastAPI, Prisma) to deliver end-to-end features in fast-paced product teams.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Frontend Engineering (React/Next.js)}: React 18/19, Next.js 15/16, TypeScript, Redux Toolkit, Zustand, TanStack Query -- building component-driven, accessible, multilingual interfaces for SaaS dashboards.

\item \textbf{AI Integration \& Applied ML}: Google Gemini API, HuggingFace Transformers, VAPI Voice AI, Label Studio -- embedding LLM-driven features, voice agents, and NLP pipelines into production web apps.

\item \textbf{SaaS \& CRM Domain}: Built multilingual admin/staff CRM dashboards (NedSwiss), real-time dashboards, and 3D visualization tools -- all under tight product/UX constraints for cross-regional operations.

\item \textbf{Backend-Adjacent (Python/Node)}: Python, FastAPI, Prisma ORM, PostgreSQL, Docker -- supporting full-stack feature delivery and data-pipeline work.

\item \textbf{Arabic Language \& Localization}: Native Arabic; experience with Arabic NLP keyword extraction, RTL interfaces, and Arabic-first AI products (Turjuman).

\item \textbf{Remote Collaboration \& Quality}: Git, feature-driven architecture, code review, Agile/Scrum -- daily collaboration with multicultural, cross-functional teams in European and MENA corporate environments.

\end{itemize}

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{Nov 2025--Present}{Front-End Developer}{RICOH Europe}{Maadi, Cairo}{}{\vspace{1pt}
\begin{itemize}
    \item Build and maintain web application features for cross-regional European operations, including an Arabic NLP keyword-extraction interface integrated with RICOH's enterprise document pipeline.
    \item Delivered multiple production frontend projects under the CORELIA umbrella: real-time tailgating anomaly detection with live MJPEG streaming, multi-mode 3D building viewer, invoice lifecycle management, and the Arabic NLP tooling above.
    \item Ship modular, reusable component systems with Shadcn UI, Radix UI, and Tailwind CSS, establishing patterns adopted across the CORELIA project portfolio.
    \item Collaborate daily with multicultural, cross-functional teams in a remote-friendly European corporate environment; communicate technical decisions clearly across disciplines.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Feb 2025--Nov 2025}{Front-End Developer}{NedSwiss}{Remote, Switzerland}{}{\vspace{1pt}
\begin{itemize}
    \item Built a multilingual admin/staff CRM dashboard with rich data tables, chart analytics, and role-based navigation -- a near-direct analog to contact-center operations interfaces.
    \item Developed a high-performance marketing website with advanced scroll animations (GSAP, Lenis) and micro-interactions, achieving smooth 60fps across devices.
    \item Implemented internationalization (next-intl), Zod-validated contact forms, and optimized bundle performance with Turbopack.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Aug 2023--Jun 2025}{Frontend Leader}{GDSC -- Shorouk Academy}{Shorouk City}{}{\vspace{1pt}
\begin{itemize}
    \item Led the frontend track for Google Developer Student Club, running workshops and hands-on sessions for 50+ students.
    \item Mentored developers in React, Next.js, TypeScript, and modern UI architecture patterns, reinforcing component-driven thinking and code review practices.
\end{itemize}}}

\end{itemize}

\section{Publications \& Open Source}
\vspace{1pt}
\begin{itemize}
\item \textbf{Maintainer} -- Turjuman: open-source AI-powered Arabic document translation platform.
\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{Bachelor of Science in Computer Science}{Shorouk Academy}{Shorouk City}{}{\vspace{1pt}
GPA: 3.8 / 4.0
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Arabic (native), English (fluent).
\end{itemize}

\section{Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{Finalist / Winner} -- WE Innovative Hackathon (2026) for CyrusLearn Interactive Learning Platform.}
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
